TITLE

### 2024-08-24 paper.qmd
Add kaggle tables.

---
title: "The Effects of Mandatory Seat Belt Laws on Driving Behavior and Traffic Fatalities"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: html
editor: visual
bibliography: references.bib
---

@@

>>>>

---
title: "The Effects of Mandatory Seat Belt Laws on Driving Behavior and Traffic Fatalities"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: 
  html:
    df-print: kable
editor: visual
bibliography: references.bib
---

@@

```{r}
library(pder)
data("SeatBelt")
head(SeatBelt)
```

### 2024-08-24 slides.qmd
Add kaggle tables.

---
title: "TITLE"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: 
  revealjs:
    chalkboard: true
    toc: true
    toc-title: "Agenda"
    toc-depth: 1
    slideNumber: true
footer: |
  <a href="paper.html" class="home-button">Home</a>
editor: visual
bibliography: references.bib
---

>>>>

---
title: "TITLE"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: 
  revealjs:
    chalkboard: true
    toc: true
    toc-title: "Agenda"
    toc-depth: 1
    slideNumber: true
    theme: black
    number-sections: true
    df-print: kable
footer: |
   <div class="custom-footer">
     <a href="paper.html" class="go-paper-button">Paper</a>
     <span style="display:inline-block; width: 200px;"></span>
     <a href="#/1" class="go-toc-button">Agenda</a>
   </div>
editor: visual
bibliography: references.bib
---
